---
title: "Assignment2_markdown"
author: "Andriy Sinclair"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("Assignment2_env.RData")

library(haven)
library(MASS)
library(dplyr)
library(modelsummary)
library(knitr)
library(broom)
```

## R Markdown

1. What is the fraction of smokers amongst male and female workers in the dataset?
```{r}
fraction_smoker
```
2. Produce a table with summary statistics (mean, standard deviation, minimum and maximum values) for all individual characteristics in the dataset, separately for smokers and non-smokers. Briefly comment on your output.

```{r}
kable(individual_summary_females, format = "markdown")
```

```{r}
kable(individual_summary_males, format = "markdown")
```



We draw the following insights from the sample:
* The average age of smokers is higher than non-smokers, the youngest smoker and non-smoker are both 18, The oldest non-smoker is older than the oldest smoker. There is more variation in age among smokers.

* A higher proportion of smokers dropped out of high school

* A higher proportion of smokers have high school as their highest level of education

* A higher proportion of smokers have some college as their highest level of education

* A higher proportion of non-smokers graduate college.

* Overall it appears non-smokers have higher educational attainment

* A higher proportion of smokers are black

* A higher percentage of non-smokers are hispanic

* A higher percentage of non-smokers are female

3. Test for differences in means of the variables colgrad and female across the
groups of smokers and non-smokers. Briefly comment on your output. [Note: you
can assume equal variances for the characteristics across the groups of smokers and
non-smokers].

```{r}
tidyttest_colgrad <- tidy(mean_test_colgrad)
tidyttest_colgrad <- dplyr::rename(tidyttest_colgrad, difference = estimate,
                           smokers = estimate1, non_smokers = estimate2)

tidyttest_female <- tidy(mean_test_female)
tidyttest_female <- dplyr::rename(tidyttest_female, difference = estimate,
                           smokers = estimate1, non_smokers = estimate2)

tidyttest_colgrad <- t(tidyttest_colgrad)
tidyttest_female <- t(tidyttest_female)

tdf <- data.frame(tidyttest_colgrad, tidyttest_female)
colnames(tdf) <- c("Colgrad", "Female")

kable(tdf, format = "markdown",
      caption = 'Difference in means for "colgrad" and "female" between smokers and non-smokers')

```



